Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-05-19 sec_ana.tex
Comments by BK for the introduction
Update on sec3 and sec4

\section{Analysis Procedure}
\label{sec:na}

@@

The ridge yield is further studied with various event selections regarding hard processes. The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity. The leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{\rm{T}}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$. The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer from the collisions to the initial partons.

Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation has been used to estimate the charged single particle efficiency and the contamination from the non-primary particle. The corrections have been tested by comparing the distributions, which are constructed with generated true particles and reconstructed particles with detector responses. The several percentage of non-closure has been considered into systematic uncertainty.

\section{Systematic Uncertainty}
\label{sec:uncertainties}

@@

\begin{table}[!h]
\centering
\caption{ Summary of the systematic uncertainties. See text for details.}
\begin{tabular}{ c|c }
%\begin{tabular}{c || c}
\hline
Source &  Uncertainty \\ \hline
Event mixing & 6-10\% \\  \hline
$\Delta\eta$ projection range & 10-15\% \\ \hline
M.C. closure & 4\% \\ \hline
Primary vertex & 4\% \\ \hline
Pileup Cut & 4\% \\ \hline
Track selection & 5\% \\ \hline
Total & 14-20\% \\
\hline
\end{tabular}
%\caption{ Definition of multiplicity class in this analysis. Reference definition of multiplicity coud be found in the following link; \url{https://twiki.cern.ch/twiki/bin/viewauth/ALICE/ReferenceMult}  }
\end{table}

>>>>

\section{Analysis Procedure}
\label{sec:an}

@@

The ridge yield is further studied with various event selections regarding hard processes. The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity. The leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{\rm{T}}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$. The transverse momentum of jet is also corrected with underlying event density($\rho \cdot A$). The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer from the collisions to the initial partons.

Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation has been used to estimate the charged single particle efficiency and the contamination from the non-primary particle.

%The corrections have been tested by comparing the distributions, which are constructed with generated true particles and reconstructed particles with detector responses. The several percentage of non-closure has been considered into systematic uncertainty.

\section{Systematic Uncertainty}
\label{sec:uncertainties}
The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and efficiency correction. Each source is separated into individual parts. The uncertainty from the event selection can be divided into Pile-up rejection and primary vertex selection. The uncertainty from the track selection is estimated by changing the selection criteria. The uncertainty from the yield extraction procedures can be divided into long-range definition and ZYAM procedure. The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to acceptance correction. Finally, The uncertainty from the application of track efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed by true particles.

\begin{table}[!h]
\caption{ The relative systematic uncertainty(\%) of the associated yield spectrum as function of $(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$(second), $\it{p}_{\rm{T,Lead}}$(thrid) or $\it{p}_{\rm{T,jet}}$(fourth) selection in high multiplicity(0-0.1\%) }
\centering
\begin{tabular}{|c|<{\centering}m{8em}|<{\centering}m{6em}|<{\centering}m{6em}|}
\hline 
Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Mixing			& $\sim$4.4	&2-8		&1-16	\\ \hline
Pileup			& $\sim$0.8	&0-4		&0-4		\\ \hline
Tracking			& $\sim$4.0 	&2		&2		\\ \hline
Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline
ZYAM			& $\sim$5.1	&2		&2		\\ \hline
$\Delta\eta$ range	& $\sim$4.5	&3-7		&3-9		\\ \hline
M.C. non-closure	& $\sim$2.5 	&1		&1		\\ \hline
Total 			& $\sim$9.7	&4-16	&4-22	\\ 
\hline 
\end{tabular}

\end{table}

@@

\iffalse

\begin{table}[!h]
\centering
\caption{ Summary of the systematic uncertainties. See text for details.}
\begin{tabular}{ c|c }
%\begin{tabular}{c || c}
\hline
Source &  Uncertainty \\ \hline
Event mixing & 6-10\% \\  \hline
$\Delta\eta$ projection range & 10-15\% \\ \hline
M.C. closure & 4\% \\ \hline
Primary vertex & 4\% \\ \hline
Pileup Cut & 4\% \\ \hline
Track selection & 5\% \\ \hline
Total & 14-20\% \\
\hline
\end{tabular}
%\caption{ Definition of multiplicity class in this analysis. Reference definition of multiplicity coud be found in the following link; \url{https://twiki.cern.ch/twiki/bin/viewauth/ALICE/ReferenceMult}  }
\end{table}
\fi
